%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Natalie}{Smith}
\title{Engineer}                               % optional, remove / comment the line if not wanted
\address{14013 Captains Row, A110}{Marina Del Rey, CA}{90292}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\phone[mobile]{+1~(234)~567~890}                   % optional, remove / comment the line if not wanted
\phone[fixed]{+1~(424)~350~1415}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{smithnm@uvic.ca}                               % optional, remove / comment the line if not wanted
\homepage{www.nataliesmith.ca}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Professional Profile}
\begin{itemize}%
	\item Skilled software developer.
	\item Angular 2 expert.
	\item Full-stack development using ruby on rails.
	\item A focus on powerful yet intuitive user interface design.
	%\item Ability to integrate hardware and software components in mechatronics systems
	\item Experienced with both unit and integration tests. 
	\item Ability to work effectively within a team setting	while also being a motivated, proactive and self-starting independent worker.
	\item Possess willingness and work ethic to learn new technologies and skills
	\item Extensive experience with customer service and practical problem-solving as well as exceptional written and verbal communication skills
\end{itemize}

\section{Technical Skills}
%\cvlistdoubleitem{C/C++}{MatLab}
\cvlistdoubleitem{HTML5/CSS3}{Javascript/jQuery}
\cvlistdoubleitem{Angular 2}{Unit Testing}
\cvlistdoubleitem{Ruby on Rails}{JSON/XML}
\cvlistdoubleitem{C/C++}{Image Processing}
\cvlistdoubleitem{C\#/.NET}{Sensor Integration}
\cvlistdoubleitem{Microcontrollers}{Control Systems}

\section{Experience}

\cventry{May 2017--Present}{Software Engineer}{QuikStor Security \& Software}{Van Nuys CA}{}{
	Responsible for front-end development of large-scale cloud web application. 
	Designed, developed and implemented page components using Angular 2.
	\begin{itemize}%
		\item Responsible for front-end development of a large-scale cloud web application.
		\item Designed, developed and implemented user-interface components using Angular 2.
		\item Created intuitve yet powerful designs using HTML, CSS3 and Typescript.
		\item Designed efficient and reliable HTTP network communication.
		\item Collaborated in a team environment.
\end{itemize}}
\newpage
\cventry{May--Aug 2015}{Undergraduate Researcher}{University of Victoria}{Victoria BC}{}{Worked in the Crystal Growth Laboratory designing a new control system for a 30 zone crystal growth furnace.
\begin{itemize}%
\item Ran experiments on the crystal growth furnace including material preparation, furnace loading, and sample testing using a Scanning Electron Microscope
\item Designed an implemented a fuzzy PID control system in LabView with adaptive control for the crystal growth furnace
\end{itemize}}
\cventry{Sept--Dec 2013}{Undergraduate Researcher}{University of Victoria}{Victoria BC}{}{Worked in the Biomedical Design and Systems Laboratory developing a medical phantom for use in testing and calibrating an ultrasound-controlled hand prosthesis.
\begin{itemize}%
	\item Designed and developed a medical phantom representing the ultrasonic properties of the tendon-hand system
	\item Tested prototypes and determined ultrasonic properties of materials
	\item Used an Ultrasonix ultrasound machine and MatLab to capture video and images of phantom prototypes
\end{itemize}}
\cventry{Jan--Apr 2013}{Clinical Engineering Co-op}{Island Health}{Victoria BC}{}{Worked in the Biomedical Engineering department of Island Health to assist in tasks such as device procurement and installation, cost analysis, preventative maintenance, and consulting with medical professionals.
\begin{itemize}%
	\item Assisted in medical device procurement and installation in hospital settings
	\item Performed cost analysis for major contract renewals
	\item Performed preventative maintenance on medical devices such as infusion pumps, defibrillators, and AEDs
	\item Consulted with medical professionals within multiple health networks across Canada in preparation for a networked fetal monitoring system
\end{itemize}}
\cventry{2011--Present}{Team Leader, Facility Attendant}{Saanich Commonwealth Place}{Victoria BC}{}{Work in supervisory roles as a Team Leader and Facility Attendant to oversee multiple staff and ensure that programs are running safely and effectively.	
\begin{itemize}%
	\item Team Leader: Directly supervise a team of lifeguards to ensure safe pool coverage, oversee first aid situations, mediate public relations situations and provide excellent internal and external customer service
	\item Facility Attendant: Responsible for overseeing all facility programs, coordinating and providing back-up for all staff and conducting emergency procedures in case of emergencies
\end{itemize}}
\section{Education}
\cventry{2011--2016}{B.Eng}{University of Victoria}{Victoria BC}{\textit{Biomedical Engineering}}{Specialization in Mechatronics}  % arguments 3 to 6 can be left empty
\section{Technical Projects}
\cvitem{NeuroJS}{Contributes to a 'deep-learning' open source project called NeuroJS. Using React and RxJS the project aims to create a real-time brain-data visualization package for bio-medical research.}
\cvitem{Web Development}{Developed multiple full stack web applications in both Ruby on Rails and Angular2. Portfolio available upon request.}
\cvitem{Mechatronics}{Designed the firmware to accomplish a conveyor belt sorting task}
\begin{itemize}%
	\item Integrated multiple sensors, actuators and motors with a micro-controller programmed in C
\end{itemize}
%\cvitem{Engineering Design}{In a team of students, designed and developed a device to mimic the breathing action of human lungs}
%\begin{itemize}%
%	\item Integrated multiple sensors and a linear actuator using a microcontroller to produce the mechanical breathing action of the device and to monitor several environmental conditions of the device such as humidity, C02 content, and temperature
%\end{itemize}
\cvitem{Neural Networks}{Designed a neural network to classify data instances in an online breast cancer database as malignant or benign}
\begin{itemize}%
	\item Used MatLab to implement a three-layer feed-forward neural network to automatically classify instances of breast cancer malignancy
\end{itemize}
\cvitem{Biomedical Image Processing}{Solved task of retinal vessel segmentation in retinal images by using MatLab to implement adaptive local thresholding by multithreshold probing}

%\section{References}
%\begin{cvcolumns}
 % \cvcolumn{Dr. Nikolai Dechev}{Associate Professor \\ University of Victoria \\ Biomedical Design and Systems Laboratory \\ 250-721-8933}
 % \cvcolumn{Dr. Kelly Stegman-Brooks}{University of Victoria \\ Biomedical Design and Systems Laboratory \\ kstegman@uvic.ca}
 % \cvcolumn{Michael Sheehan}{Program Technician \\ Saanich Commonwealth Place \\ 250-475-7607}
%\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\section{References}
\begin{cvcolumns}
	\cvcolumn{Dr. Nikolai Dechev}{
		\begin{itemize}
			\item Associate Professor.
			\item University of Victoria
			\item Biomedical Design and Systems
			Laboratory
			\item Phone:~250~721-8933
	\end{itemize}}
	\cvcolumn{Dr. Kelly Stegman-Brooks}{
		\begin{itemize}
			\item University of Victoria
			\item Biomedical Design and Systems
			Laboratory
			\item Email:~kstegman@uvic.ca
	\end{itemize}}
	\cvcolumn{Michael Sheehan}{
		\begin{itemize}
			\item Program Technician
			\item Saanich Commonwealth Place
			\item Phone:~250~475-7607 
	\end{itemize}}
\end{cvcolumns}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\end{document}


%%%%%%% Cyber Coder Questions %%%%%%
% Please tell me the details of your most recent salary (base, bonus, commission, etc.) and your ideal salary for this position?
%My current salary is an annual rate of $55,000. I believe this to be below industry standard for my skills and experience. For such a role as this I would be looking for $70,000 to $80,000 per year.




%% end of file `template.tex'.
